How many researchers use 'boilerplate' statistical analysis sections?

### 2020-09-02 manuscript/draft_manuscript.Rmd
update draft manuscript

We compiled an extensive list of common methods and related terminology as a way of standardising descriptions of statistical analyses undertaken. An initial list was compiled by calculating individual word frequencies in the data and identifying relevant terms that appeared at least 100 times. Additional terms were added based on index searches of statistical textbooks [TODO need to mention this here? If so, add references] and spell checks (e.g. ‘fischer’ instead of ‘fisher’). Using the final list, we performed multiple searches to identify possible variants of each term and replaced these with a standardised spelling. For example, instances ‘chi square’ and ‘chi squared’ were replaced with ‘chi-square’. Other variants of terminology considered plurals (e.g. chi squares), combinations of characters and numbers (e.g. chi 2) and combined text (e.g. chisquare).

As a final step, common stop words including pronouns, contractions and selected prepositions were removed from the data. Stop words were identified from lists available from the ‘tm’ R package (Supplementary File 2). We chose to keep some prepositions included in the available list to minimise potential changes to the context of statistical method(s) being described (e.g. ‘between’, ‘against’).

<!-- ```{r echo=F,fig.cap='\\label{fig:search-strategy}Search strategy',fig.align='center',fig.height=5} -->
<!-- knitr::include_graphics("search_strategy.png") -->

>>>>

We compiled an extensive list of common methods and statistical terminology to standardise descriptions of statistical analyses undertaken. An initial list was compiled by calculating individual word frequencies in the data and identifying relevant terms. Additional terms were added based on index searches of statistical textbooks [TODO need to mention this here? If so, add references] and spelling checks (e.g. ‘fischer’ instead of ‘fisher’). Multiple searches were then performed to identify possible variants of list terms, which were replaced with a standardised spelling. For example, instances ‘chi square’ and ‘chi squared’ were replaced with ‘chi-square’. Other variants of terminology considered plurals (e.g. chi squares), combinations of characters and numbers (e.g. chi 2) and combined text (e.g. chisquare).

As a final step, common stop words including pronouns, contractions and selected prepositions were removed from the data. We chose to retain selected stop words that, if excluded, may have changed the context of statistical method(s) being described (e.g. ‘between’, ‘against’).
